To run the differential expression analysis first calculate the pseudobulked aggregate expression at the biological replicate level.
Load packages.
```{r warning=FALSE, message=FALSE}
library(Seurat)
library(SeuratDisk)
```
Load dLN data.
```{r}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_04")
dLN_data <- LoadH5Seurat("dLN_data.h5seurat")
```
Assign mouse information to dLN object.
```{r}
library(openxlsx)
ann_D0 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D0")
ann_D1 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D1")
ann_D3 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D3")
ann_D5 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D5")
ann_D7 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D7")
ann_D30 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D30")

dLN_data@meta.data$mouseID = ""
dLN_data@meta.data$mousetag = ""

MouseID <- c()
Mousetag <- c()

ann_D1_1 <- ann_D1[1:7,] 
ann_D1_2 <- ann_D1[8:14,] 

for(k in dLN_data@meta.data$orig.id){
  if (nchar(k) == 7) {
    if (substr(k,1,2) == "D0") {
      MouseID = c(MouseID, ann_D0$MouseID[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D0$Mousetag[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D1") {
      #dLN 
      if (substr(k,1,4) == "D105") {
        MouseID = c(MouseID, ann_D1_1$MouseID[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_1$Mousetag[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      if (substr(k,1,4) == "D106") {
        MouseID = c(MouseID, ann_D1_1$MouseID[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_1$Mousetag[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      
      if (substr(k,1,4) == "D107") {
        MouseID = c(MouseID, ann_D1_2$MouseID[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_2$Mousetag[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      if (substr(k,1,4) == "D108") {
        MouseID = c(MouseID, ann_D1_2$MouseID[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_2$Mousetag[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
    }
    
    if (substr(k,1,2) == "D3") {
      MouseID = c(MouseID, ann_D3$MouseID[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D3$Mousetag[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D5") {
      MouseID = c(MouseID, ann_D5$MouseID[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D5$Mousetag[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D7") {
      MouseID = c(MouseID, ann_D7$MouseID[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D7$Mousetag[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
  }
  
  if (nchar(k) == 8) {
    if (substr(k,1,3) == "D30") {
      MouseID = c(MouseID, ann_D30$MouseID[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
      Mousetag = c(Mousetag, ann_D30$Mousetag[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
    }
  }
}

dLN_data@meta.data$mouseID = MouseID
dLN_data@meta.data$mousetag = Mousetag

dLN_data@meta.data$mouseID_time <- paste(dLN_data@meta.data$timepoint, dLN_data@meta.data$mouseID, sep = "_")
dLN_data@meta.data$mouseID_time_cluster <- paste(dLN_data@meta.data$mouseID_time, 
                                                 dLN_data@meta.data$cluster_symbol, sep = "_")
```

Calculate sum aggregated Seurat object.
```{r}
#library(Seurat)
#library(ggplot2)

dLN_data@meta.data$cluster_symbol1 <- as.character(dLN_data@meta.data$cluster_symbol)

dLN_aggregate <- Seurat:::PseudobulkExpression(dLN_data, return.seurat = TRUE, assay = "RNA", 
                                               pb.method = 'aggregate', slot = 'counts',
                                               group.by = c('mouseID_time', 'cluster_symbol1'))
# Keep the sample names in metadata 
samples <- as.character(dLN_aggregate@assays$RNA@counts@Dimnames[[2]])
dLN_aggregate@meta.data$Samples <- samples
```

Reassign the time sex and vaccine and mouse_id information to the aggregated data.
```{r}
dLN_aggregate@meta.data$vax = ""
dLN_aggregate@meta.data$sex = ""
dLN_aggregate@meta.data$time = ""
dLN_aggregate@meta.data$cluster = ""

t <- c()
sex <- c()
vax <- c()
cluster <- c()

for (j in 1:length(dLN_aggregate@meta.data$Sample)) {
  Str <- strsplit(dLN_aggregate@meta.data$Sample[j], split = "_")
  t <- c(t, Str[[1]][1])
  vax <- c(vax, Str[[1]][3])
  sex <- c(sex, Str[[1]][4])
  cluster <- c(cluster, Str[[1]][6])
}
dLN_aggregate@meta.data$crude_time <- t
dLN_aggregate@meta.data$sex <- sex
dLN_aggregate@meta.data$vax <- vax
dLN_aggregate@meta.data$cluster <- cluster

# Replace D0 with Dneg and Dint in internal control vipex and naive
time <- dLN_aggregate@meta.data$crude_time

for (i in 1:length(time)) {
  if (dLN_aggregate@meta.data$vax[i] == "naïve") {
    time[i] <- "Dneg"
  }
  if (dLN_aggregate@meta.data$vax[i] == "vipex") {
    time[i] <- "Dint"
  }
}

dLN_aggregate@meta.data$time <- time
```

Save aggregated Seurat object for future use.
```{r}
setwd('C:/Users/budha/Documents/R/YF_complete/YF_report_10')
SaveH5Seurat(dLN_aggregate, filename = "dLN_aggregate.h5seurat", overwrite = TRUE, verbose = FALSE)
```

Now PBMC. Get the file and convert to aggregate.
Load data.
```{r}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_04")
PBMC_data <- LoadH5Seurat("PBMC_data.h5seurat")
```
Assign mouseid information on the PBMC Seurat object.
```{r}
library(openxlsx)
ann_D0 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D0")
ann_D1 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D1")
ann_D3 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D3")
ann_D5 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D5")
ann_D7 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D7")
ann_D30 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D30")

PBMC_data@meta.data$mouseID = ""
PBMC_data@meta.data$mousetag = ""

MouseID <- c()
Mousetag <- c()

ann_D1_1 <- ann_D1[1:7,] 
ann_D1_2 <- ann_D1[8:14,] 

for(k in PBMC_data@meta.data$orig.id){
  if (nchar(k) == 7) {
    if (substr(k,1,2) == "D0") {
      MouseID = c(MouseID, ann_D0$MouseID[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D0$Mousetag[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D1") {
      #PBMC 
      if (substr(k,1,4) == "D101") {
        MouseID = c(MouseID, ann_D1_1$MouseID[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_1$Mousetag[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      if (substr(k,1,4) == "D102") {
        MouseID = c(MouseID, ann_D1_1$MouseID[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_1$Mousetag[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      
      if (substr(k,1,4) == "D103") {
        MouseID = c(MouseID, ann_D1_2$MouseID[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_2$Mousetag[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      if (substr(k,1,4) == "D104") {
        MouseID = c(MouseID, ann_D1_2$MouseID[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_2$Mousetag[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
    }
    
    if (substr(k,1,2) == "D3") {
      MouseID = c(MouseID, ann_D3$MouseID[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D3$Mousetag[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D5") {
      MouseID = c(MouseID, ann_D5$MouseID[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D5$Mousetag[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D7") {
      MouseID = c(MouseID, ann_D7$MouseID[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D7$Mousetag[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
  }
  
  if (nchar(k) == 8) {
    if (substr(k,1,3) == "D30") {
      MouseID = c(MouseID, ann_D30$MouseID[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
      Mousetag = c(Mousetag, ann_D30$Mousetag[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
    }
  }
}

PBMC_data@meta.data$mouseID = MouseID
PBMC_data@meta.data$mousetag = Mousetag

PBMC_data@meta.data$mouseID_time <- paste(PBMC_data@meta.data$timepoint, PBMC_data@meta.data$mouseID, sep = "_")
```

Calculate sum aggregated Seurat object on time_sex_vax_mouseid information.
```{r}
PBMC_data@meta.data$cluster_symbol1 <- as.character(PBMC_data@meta.data$cluster_symbol)

PBMC_aggregate <- Seurat:::PseudobulkExpression(PBMC_data, return.seurat = TRUE, assay = "RNA", 
                                               pb.method = 'aggregate', slot = 'counts',
                                               group.by = c('mouseID_time', 'cluster_symbol1'))
# Keep the sample names in metadata 
samples <- as.character(PBMC_aggregate@assays$RNA@counts@Dimnames[[2]])
PBMC_aggregate@meta.data$Samples <- samples
```

Assign the metadata to aggregated Seurat object.
```{r}
PBMC_aggregate@meta.data$vax = ""
PBMC_aggregate@meta.data$sex = ""
PBMC_aggregate@meta.data$time = ""
PBMC_aggregate@meta.data$cluster = ""

t <- c()
sex <- c()
vax <- c()
cluster <- c()

for (j in 1:length(PBMC_aggregate@meta.data$Sample)) {
  Str <- strsplit(PBMC_aggregate@meta.data$Sample[j], split = "_")
  t <- c(t, Str[[1]][1])
  vax <- c(vax, Str[[1]][3])
  sex <- c(sex, Str[[1]][4])
  cluster <- c(cluster, Str[[1]][6])
}
PBMC_aggregate@meta.data$crude_time <- t
PBMC_aggregate@meta.data$sex <- sex
PBMC_aggregate@meta.data$vax <- vax
PBMC_aggregate@meta.data$cluster <- cluster

# Replace D0 with Dneg and Dint in internal control vipex and naive
time <- PBMC_aggregate@meta.data$crude_time

for (i in 1:length(time)) {
  if (PBMC_aggregate@meta.data$vax[i] == "naïve") {
    time[i] <- "Dneg"
  }
  if (PBMC_aggregate@meta.data$vax[i] == "vipex") {
    time[i] <- "Dint"
  }
}

PBMC_aggregate@meta.data$time <- time
```

Save aggregated Seurat object for future use.
```{r}
setwd('C:/Users/budha/Documents/R/YF_complete/YF_report_10')
SaveH5Seurat(PBMC_aggregate, filename = "PBMC_aggregate.h5seurat", overwrite = TRUE, verbose = FALSE)
```

Now spleen. Get the file and convert to aggregate.
Load data.
```{r}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_04")
spleen_data <- LoadH5Seurat("spleen_data.h5seurat")
```

Assign mouseid information on the spleen Seurat object.
```{r}
library(openxlsx)
ann_D0 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D0")
ann_D1 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D1")
ann_D3 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D3")
ann_D5 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D5")
ann_D7 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D7")
ann_D30 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D30")

spleen_data@meta.data$mouseID = ""
spleen_data@meta.data$mousetag = ""

MouseID <- c()
Mousetag <- c()

ann_D1_1 <- ann_D1[1:7,] 
ann_D1_2 <- ann_D1[8:14,] 

for(k in spleen_data@meta.data$orig.id){
  if (nchar(k) == 7) {
    if (substr(k,1,2) == "D0") {
      MouseID = c(MouseID, ann_D0$MouseID[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D0$Mousetag[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D1") {
      #spleen 
      if (substr(k,1,4) == "D109") {
        MouseID = c(MouseID, ann_D1_1$MouseID[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_1$Mousetag[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      if (substr(k,1,4) == "D110") {
        MouseID = c(MouseID, ann_D1_1$MouseID[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_1$Mousetag[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      
      if (substr(k,1,4) == "D111") {
        MouseID = c(MouseID, ann_D1_2$MouseID[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_2$Mousetag[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      if (substr(k,1,4) == "D112") {
        MouseID = c(MouseID, ann_D1_2$MouseID[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_2$Mousetag[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
    }
    
    if (substr(k,1,2) == "D3") {
      MouseID = c(MouseID, ann_D3$MouseID[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D3$Mousetag[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D5") {
      MouseID = c(MouseID, ann_D5$MouseID[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D5$Mousetag[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D7") {
      MouseID = c(MouseID, ann_D7$MouseID[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D7$Mousetag[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
  }
  
  if (nchar(k) == 8) {
    if (substr(k,1,3) == "D30") {
      MouseID = c(MouseID, ann_D30$MouseID[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
      Mousetag = c(Mousetag, ann_D30$Mousetag[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
    }
  }
}

spleen_data@meta.data$mouseID = MouseID
spleen_data@meta.data$mousetag = Mousetag

spleen_data@meta.data$mouseID_time <- paste(spleen_data@meta.data$timepoint, spleen_data@meta.data$mouseID, sep = "_")
```

Calculate sum aggregated Seurat object.
```{r}
spleen_data@meta.data$cluster_symbol1 <- as.character(spleen_data@meta.data$cluster_symbol)

spleen_aggregate <- Seurat:::PseudobulkExpression(spleen_data, return.seurat = TRUE, assay = "RNA", 
                                               pb.method = 'aggregate', slot = 'counts',
                                               group.by = c('mouseID_time', 'cluster_symbol1'))
# Keep the sample names in metadata 
samples <- as.character(spleen_aggregate@assays$RNA@counts@Dimnames[[2]])
spleen_aggregate@meta.data$Samples <- samples
```

Assign the metadata to aggregated Seurat object.
```{r}
spleen_aggregate@meta.data$vax = ""
spleen_aggregate@meta.data$sex = ""
spleen_aggregate@meta.data$time = ""
spleen_aggregate@meta.data$cluster = ""

t <- c()
sex <- c()
vax <- c()
cluster <- c()

for (j in 1:length(spleen_aggregate@meta.data$Sample)) {
  Str <- strsplit(spleen_aggregate@meta.data$Sample[j], split = "_")
  t <- c(t, Str[[1]][1])
  vax <- c(vax, Str[[1]][3])
  sex <- c(sex, Str[[1]][4])
  cluster <- c(cluster, Str[[1]][6])
}
spleen_aggregate@meta.data$crude_time <- t
spleen_aggregate@meta.data$sex <- sex
spleen_aggregate@meta.data$vax <- vax
spleen_aggregate@meta.data$cluster <- cluster

# Replace D0 with Dneg and Dint in internal control vipex and naive
time <- spleen_aggregate@meta.data$crude_time

for (i in 1:length(time)) {
  if (spleen_aggregate@meta.data$vax[i] == "naïve") {
    time[i] <- "Dneg"
  }
  if (spleen_aggregate@meta.data$vax[i] == "vipex") {
    time[i] <- "Dint"
  }
}

spleen_aggregate@meta.data$time <- time
```
Save aggregated Seurat object for future use.
```{r}
setwd('C:/Users/budha/Documents/R/YF_complete/YF_report_10')
SaveH5Seurat(spleen_aggregate, filename = "spleen_aggregate.h5seurat", overwrite = TRUE, verbose = FALSE)
```

Now ndLN. Get the file and convert to aggregate.
Load data.
```{r}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_04")
ndLN_data <- LoadH5Seurat("ndLN_data.h5seurat")
```
Assign mouseid information on the ndLN Seurat object.
```{r}
library(openxlsx)
ann_D0 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D0")
ann_D1 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D1")
ann_D3 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D3")
ann_D5 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D5")
ann_D7 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D7")
ann_D30 <- read.xlsx('time_sex_vax_mouseid.xlsx', sheet = "D30")

ndLN_data@meta.data$mouseID = ""
ndLN_data@meta.data$mousetag = ""

MouseID <- c()
Mousetag <- c()

ann_D1_1 <- ann_D1[1:7,] 
ann_D1_2 <- ann_D1[8:14,] 

for(k in ndLN_data@meta.data$orig.id){
  if (nchar(k) == 7) {
    if (substr(k,1,2) == "D0") {
      MouseID = c(MouseID, ann_D0$MouseID[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D0$Mousetag[ann_D0$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D1") {
      #ndLN 
      if (substr(k,1,4) == "D115") {
        MouseID = c(MouseID, ann_D1_1$MouseID[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_1$Mousetag[ann_D1_1$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
      
      if (substr(k,1,4) == "D116") {
        MouseID = c(MouseID, ann_D1_2$MouseID[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
        Mousetag = c(Mousetag, ann_D1_2$Mousetag[ann_D1_2$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      }
    }
    
    if (substr(k,1,2) == "D3") {
      MouseID = c(MouseID, ann_D3$MouseID[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D3$Mousetag[ann_D3$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D5") {
      MouseID = c(MouseID, ann_D5$MouseID[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D5$Mousetag[ann_D5$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
    
    if (substr(k,1,2) == "D7") {
      MouseID = c(MouseID, ann_D7$MouseID[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
      Mousetag = c(Mousetag, ann_D7$Mousetag[ann_D7$GEX.Hash.tag == as.numeric(substr(k,6,7))])
    }
  }
  
  if (nchar(k) == 8) {
    if (substr(k,1,3) == "D30") {
      MouseID = c(MouseID, ann_D30$MouseID[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
      Mousetag = c(Mousetag, ann_D30$Mousetag[ann_D30$GEX.Hash.tag == as.numeric(substr(k,7,8))])
    }
  }
}

ndLN_data@meta.data$mouseID = MouseID
ndLN_data@meta.data$mousetag = Mousetag

ndLN_data@meta.data$mouseID_time <- paste(ndLN_data@meta.data$timepoint, ndLN_data@meta.data$mouseID, sep = "_")
```

Set the metadata and generate the aggregate object.
```{r}
ndLN_data@meta.data$cluster_symbol1 <- as.character(ndLN_data@meta.data$cluster_symbol)

ndLN_aggregate <- Seurat:::PseudobulkExpression(ndLN_data, return.seurat = TRUE, assay = "RNA", 
                                               pb.method = 'aggregate', slot = 'counts',
                                               group.by = c('mouseID_time', 'cluster_symbol1'))
# Keep the sample names in metadata 
samples <- as.character(ndLN_aggregate@assays$RNA@counts@Dimnames[[2]])
ndLN_aggregate@meta.data$Samples <- samples
```
Assign the metadata to aggregated Seurat object.
```{r}
ndLN_aggregate@meta.data$vax = ""
ndLN_aggregate@meta.data$sex = ""
ndLN_aggregate@meta.data$time = ""
ndLN_aggregate@meta.data$cluster = ""

t <- c()
sex <- c()
vax <- c()
cluster <- c()

for (j in 1:length(ndLN_aggregate@meta.data$Sample)) {
  Str <- strsplit(ndLN_aggregate@meta.data$Sample[j], split = "_")
  t <- c(t, Str[[1]][1])
  vax <- c(vax, Str[[1]][3])
  sex <- c(sex, Str[[1]][4])
  cluster <- c(cluster, Str[[1]][6])
}
ndLN_aggregate@meta.data$crude_time <- t
ndLN_aggregate@meta.data$sex <- sex
ndLN_aggregate@meta.data$vax <- vax
ndLN_aggregate@meta.data$cluster <- cluster

# Replace D0 with Dneg and Dint in internal control vipex and naive
time <- ndLN_aggregate@meta.data$crude_time

for (i in 1:length(time)) {
  if (ndLN_aggregate@meta.data$vax[i] == "naïve") {
    time[i] <- "Dneg"
  }
  if (ndLN_aggregate@meta.data$vax[i] == "vipex") {
    time[i] <- "Dint"
  }
}

ndLN_aggregate@meta.data$time <- time
```
Save aggregated Seurat object for future use.
```{r}
setwd('C:/Users/budha/Documents/R/YF_complete/YF_report_10')
SaveH5Seurat(ndLN_aggregate, filename = "ndLN_aggregate.h5seurat", overwrite = TRUE, verbose = FALSE)
```
