This markdown calls the saved aggregated Seurat objects from DE_code_01.Rmd.
It also uses the whole data Seurat objects from DE_code_01 containing the biological replicate level metadata.
Then it performs the DESeq analysis on them.
It saves the Benjamini-Hochberg corrected outputs.

Load packages.
```{r}
library(Seurat)
library(SeuratDisk)
library(DESeq2)
library(openxlsx)
```
First read the excel files with the details of clusters and cells.
```{r}
dLN_gist <- read.xlsx("C:/Users/budha/Documents/R/YF_complete/YF_report_04/ver3/supplementary_file_03.xlsx", sheet = "dLN")
spleen_gist <- read.xlsx("C:/Users/budha/Documents/R/YF_complete/YF_report_04/ver3/supplementary_file_03.xlsx", sheet = "spleen")
PBMC_gist <- read.xlsx("C:/Users/budha/Documents/R/YF_complete/YF_report_04/ver3/supplementary_file_03.xlsx", sheet = "PBMC")
ndLN_gist <- read.xlsx("C:/Users/budha/Documents/R/YF_complete/YF_report_04/ver3/supplementary_file_03.xlsx", sheet = "ndLN")
```

Load dLN aggregated object. dLN_data with the replicate metadata should be in the environment already.
```{r warning=FALSE, message=FALSE}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_10")
dLN_aggregate <- LoadH5Seurat("dLN_aggregate.h5seurat")
```

Load spleen aggregated object. spleen_data with the replicate metadata should be in the environment already.
```{r warning=FALSE, message=FALSE}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_10")
spleen_aggregate <- LoadH5Seurat("spleen_aggregate.h5seurat")
```

Load PBMC aggregated object. PBMC_data with the replicate metadata should be in the environment already.
```{r warning=FALSE, message=FALSE}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_10")
PBMC_aggregate <- LoadH5Seurat("PBMC_aggregate.h5seurat")
```

Load ndLN aggregated object. ndLN_data with the replicate metadata should be in the environment already.
```{r warning=FALSE, message=FALSE}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_10")
ndLN_aggregate <- LoadH5Seurat("ndLN_aggregate.h5seurat")
```

Execute DESeq. 
Keep the Benjamini-Hochberg corrcted outputs.
```{r warning=FALSE, message=FALSE}
DESEq_wrap <- function(testtemp1, cellgist, whole4SCT) {
# Get the data in a temporary variable
#testtemp1 <- dLN_aggregate
#cellgist <- dLN_gist
#whole4SCT <- dLN_data

# Remove naive
testtemp1 <- subset(testtemp1, subset = time != "Dneg")

# Keep the genes in the SCT in the RNA, remove the rest
counts_RNA <- GetAssayData(testtemp1, assay = "RNA")
rownames_SCT <- rownames(GetAssayData(whole4SCT, assay = "SCT"))
counts_RNA <- counts_RNA[(which(rownames(counts_RNA) %in% rownames_SCT)),]
testtemp1 <- subset(testtemp1, features = rownames(counts_RNA))

# Rename the vipex 
vax <- testtemp1@meta.data$vax 
for (i in 1:length(vax)) {
  if (vax[i] == "Vipex") {
    vax[i] <- "vipex"
  }
}

testtemp1@meta.data$vax <- vax
# Rename the vipex timepoints
time <- testtemp1@meta.data$time
for (j in 1:length(time)) {
  if (time[j] == "D0") {
    time[j] <- "D"
  }
  if (time[j] == "Dint") {
    time[j] <- "D"
  }
}

testtemp1@meta.data$time <- time

testtemp1@meta.data$time_sex_vax_clust <- paste(testtemp1@meta.data$time, testtemp1@meta.data$sex, 
                                            testtemp1@meta.data$vax, testtemp1@meta.data$cluster, sep = "_")

# modify gist
cellgist <- cellgist[-which(cellgist$Vax=="naïve"),]
row.names(cellgist) <- NULL

m <- 1
DEG_list_bonferroni <- list()
DEG_list_benjamini <- list()
#i <- 1
for (i in which(!(cellgist$Time %in% c("D0", "Dint")))) { # time-sex-vax 
  print(i)
  # first check if it is a male entry or a female entry
  if (cellgist$Sex[i] == "M") {
    vipex_entry <-which(cellgist$Time %in% c("D0", "Dint"))[which(cellgist$Sex[which(cellgist$Time %in% c("D0", "Dint"))]=="M")]
    SEX <- "male"
  }
  if (cellgist$Sex[i] == "F") {
    vipex_entry <-which(cellgist$Time %in% c("D0", "Dint"))[which(cellgist$Sex[which(cellgist$Time %in% c("D0", "Dint"))]=="F")]
    SEX <- "female"
  }
  #j <- 1
  for (j in 1:45) { # cluster #45
    
    # First check if the vipex has more than 50 cells
    if (sum(cellgist[vipex_entry,j+3]) < 50) {
      next
    }
    
    # Then check the number of cells in the test time-sex-vax-clust overall
    if (cellgist[i,j+3] <= 30) {
      next
    }
    if (cellgist[i,j+3] > 30) {
    
    # Execute DEG analysis
    Idents(testtemp1) <- "time_sex_vax_clust"
    DefaultAssay(testtemp1) <- "RNA"
    
    ident1 = paste("D", SEX, "vipex", colnames(cellgist)[j+3], sep = "_") # control
    ident2 = paste(cellgist[i,1], SEX, strsplit(cellgist$Vax[i], split = " ")[[1]][2], colnames(cellgist)[j+3], sep = "_") 
    
    print(ident1)
    print(ident2)
    
    cells1 <- WhichCells(object = testtemp1, idents = ident1) # control
    cells2 <- WhichCells(object = testtemp1, idents = ident2)
    
    # here test whether the biological replicates have adequate number of cells (15 cells at least)
    # move ahead with 2 or more samples in both, skip otherwise
    cells1_depth <- c()
    for (p in 1:length(cells1)) {
      cells1_depth <- c(cells1_depth, sum(whole4SCT$mouseID_time_cluster == cells1[p]))
    }
    names(cells1_depth) <- cells1
    cells1_depth <- cells1_depth[which(cells1_depth >= 15)]
    Cell1 <- names(cells1_depth)
    
    cells2_depth <- c()
    for (p in 1:length(cells2)) {
      cells2_depth <- c(cells2_depth, sum(whole4SCT$mouseID_time_cluster == cells2[p]))
    }
    names(cells2_depth) <- cells2
    cells2_depth <- cells2_depth[which(cells2_depth >= 15)]
    Cell2 <- names(cells2_depth)
    
    if ((length(Cell1) >= 2) && (length(Cell2) >= 2)) {
    
    # deseq group info
    group.info <- data.frame(row.names = c(Cell1, Cell2))
    group.info[cells1, "group"] <- "Group1" # control
    group.info[cells2, "group"] <- "Group2" 
    group.info[, "group"] <- factor(x = group.info[, "group"])
    group.info$wellKey <- rownames(x = group.info)
    
    # data matrix
    #data.use <-  as.matrix(GetAssayData(object = testtemp1, slot = "count"))
    data.use <-  GetAssayData(object = testtemp1, slot = "count")
    data.use <- data.use[, rownames(x = group.info), drop = FALSE]
    
    # Execute DESeq
    dds1 <- DESeq2::DESeqDataSetFromMatrix(
    countData = data.use,
    colData = group.info,
    design = ~ group
    )
    dds1 <- DESeq(dds1, fitType = "local", quiet = TRUE)
    
    # Benjamini
    res_BH <- DESeq2::results(
    object = dds1,
    pAdjustMethod = "BH"
    )
    
    # Fold change shrinking
    resLFC <- lfcShrink(dds1, coef = resultsNames(dds1)[2], type = "apeglm", quiet = TRUE)
    
    # generate result data frames
    # Benjamini
    to.return.ben <- data.frame()
    to.return.ben <- data.frame(genes = rownames(res_BH), cluster = rep(colnames(cellgist)[j+3], length(res_BH$pvalue)),
                            baseline = res_BH$baseMean, fc = res_BH$log2FoldChange, LFC_sh = resLFC$log2FoldChange,
                            p_val = res_BH$pvalue, p_adj = res_BH$padj)
    
    
    # filter on adjuster p-value and fold change
    # Benjamini
    to.return.ben <- to.return.ben[to.return.ben$p_adj<0.1,]
    to.return.ben <- to.return.ben[abs(to.return.ben$LFC_sh)>0.25,]
    to.return.ben <- to.return.ben[-which(is.na(to.return.ben$p_val)),]
    
    # Concatenate
    # Benjamini
    if (j == 1) {
      bde_ben <- to.return.ben
    } else {
      bde_ben <- rbind(bde_ben, to.return.ben)
    }
  
    }
    }
  }
  DEG_list_benjamini[[m]] <- bde_ben
  m <- m + 1
}

return(DEG_list_benjamini)
}
```

Carry out DESeq for four tissues.
```{r}
dLN_DEG_list <- DESEq_wrap(dLN_aggregate, dLN_gist, dLN_data)
PBMC_DEG_list <- DESEq_wrap(PBMC_aggregate, PBMC_gist, PBMC_data)
spleen_DEG_list <- DESEq_wrap(spleen_aggregate, spleen_gist, spleen_data)
ndLN_DEG_list <- DESEq_wrap(ndLN_aggregate, ndLN_gist, ndLN_data)
```
Save the DEG lists.
```{r}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_10")
save(ndLN_DEG_list, file = "ndLN_DEG_list.rda")
save(dLN_DEG_list, file = "dLN_DEG_list.rda")
save(PBMC_DEG_list, file = "PBMC_DEG_list.rda")
save(spleen_DEG_list, file = "spleen_DEG_list.rda")
```

