Validation figures.
1. Querec et al., 2006
2. Gaucher et al., 2008
3. Querec et al., 2008
4. Costa Neves et al., 2009
5. Marquardt et al., 2015
6. Hou et al., 2017
7. Mantel et al., 2024

We attempt to recapitulate the results from previous papers. We start with Querec et al 2006.
In Querec et al., the authors report that 
1. CD80, CD40, CD86, IL6, TNF-a, IL-10 are upregulated in MoDCs day 3 day 5, PBMC. Human. Similar to cDC.
2. IFN alpha in pDC, PBMC. Day 3 and 5, Human. PBMC.
3. IL-12p40, IL-6 are upregulated in CD11c+ DCs from spleen, day 1, 3 day 5. Mouse.
4. CD80, CD40, CD86, I-Ab upregulated in CD11c+ DCs from dLN, day 1, 3. Mouse.
5. Less important (because separately treated): CD4+ and CD8+ cells IFN-gamma, IL-4, IL-5, IL-13. Day 1, 3, 5, 7, 30. MOuse.

Load packages.
```{r}
library(Seurat)
library(SeuratDisk)
library(ggplot2)
library(ggpubr)
```

Load data.
```{r}
setwd("./Data/Aggregated_objects")

dLN_aggre <- readRDS("dLN_aggre.rds")
spleen_aggre <- readRDS("spleen_aggre.rds")
PBMC_aggre <- readRDS("PBMC_aggre.rds")
ndLN_aggre <- readRDS("ndLN_aggre.rds")
```
Normalize the aggregate data. Expression of genes when all counts are pulled from the respective clusters.
```{r}
dLN_aggre <- NormalizeData(dLN_aggre)
spleen_aggre <- NormalizeData(spleen_aggre)
PBMC_aggre <- NormalizeData(PBMC_aggre)
ndLN_aggre <- NormalizeData(ndLN_aggre)
```


```{r}
# pull out PBMC, cDCs, vipex and good-vax
Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "d1")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30")
temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5")
temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
#temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")
temp3@meta.data$time_vax <- factor(temp3@meta.data$time_vax, levels = c("Dneg_naïve", "D0_Vipex ", "D3_YF good"))
Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Cd80", pt.size = 0, cols = c("#00b681","#9c9c9c","#143fff")) + stat_compare_means()#+
#stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
#DefaultAssay(temp3) <- "SCT"
#VlnPlot(temp3, features = "Cd80", pt.size = 0) #+
#stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)

DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Cd86", pt.size = 0, cols = c("#00b681","#9c9c9c","#143fff")) + stat_compare_means()#+
#stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
#DefaultAssay(temp3) <- "SCT"
#VlnPlot(temp3, features = "Cd86", pt.size = 0) #+
#stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)

DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Tnf",  pt.size = 0, cols = c("#00b681","#9c9c9c","#143fff")) + stat_compare_means() #+
#stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
#DefaultAssay(temp3) <- "SCT"
#VlnPlot(temp3, features = "Tnf", pt.size = 0) #+
#stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)


# pull vipex and day 1, vipex and day 3, vipex and day 5

# plot CD80, CD40, CD86, IL6, TNF-a, IL-10


Idents(spleen_aggre) <- "cluster" 
temp1 <- subset(spleen_aggre, idents = "d2")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30")
temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5")
temp2 <- subset(temp2, subset = time != "D3")
temp3 <- subset(temp2, subset = vax != "vipex")
#temp3 <- subset(temp3, subset = vax != "naïve")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Il12b", pt.size = 0, cols = rep("grey",4))

Idents(dLN_aggre) <- "cluster" 
temp1 <- subset(dLN_aggre, idents = "d1")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30")
temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5")
temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
#temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")
temp3@meta.data$time_vax <- factor(temp3@meta.data$time_vax, levels = c("Dneg_naïve", "D0_Vipex ", "D3_YF good"))
Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Cd80", pt.size = 0, cols = c("#00b681","#9c9c9c","#143fff")) + stat_compare_means()
VlnPlot(temp3, features = "Cd40", pt.size = 0, cols = c("#00b681","#9c9c9c","#143fff")) + stat_compare_means()


Idents(dLN_aggre) <- "cluster" 
temp1 <- subset(dLN_aggre, idents = "n1")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30")
temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5")
temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
#temp3 <- subset(temp3, subset = vax != "naïve")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Ifng", pt.size = 0, cols = rep("grey",4))

Idents(dLN_aggre) <- "cluster" 
temp1 <- subset(dLN_aggre, idents = paste(greeks('tau'),5, sep = ""))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30")
temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5")
temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "YF bad")
#temp3 <- subset(temp3, subset = vax != "naïve")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")
temp3@meta.data$time_vax <- factor(temp3@meta.data$time_vax, levels = c("Dneg_naïve", "D0_Vipex ", "D3_YF good"))
Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Ifng", pt.size = 0, cols = c("#00b681","#9c9c9c","#143fff")) + stat_compare_means()


```
Next attempt is Gaucher et al., 2008.
1. Look at the following gene expression on Day 1, 3, 5, besides naive and vipex.
IFN-induced, TLR associated:
Aim2, G1p2, G1p3, Gbp1, Gbp2, Ifi27, Ifi30, Mx1, Mx2, Oas1, Oas2, Oas3, Sp110, Trim21, Trim22, Trim5, Il15, Irf7, Myd88, Ticam1, Tlr7
```{r}
features <- c("Aim2", "Isg15", "Gbp2", "Gbp2b", "Ifi27", "Ifi30", "Oas3", "Sp110", "Trim21", "Trim5", "Il15", "Irf7", "Myd88", "Ticam1", "Tlr7")
Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D0")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "naïve")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D0")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "Vipex ")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D3")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D3")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF bad")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D5")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D5")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF bad")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),10, sep = ""))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Gbp2", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
#VlnPlot(temp3, features = "Ifi27", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('nu'),1, sep = ""))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Il15", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Myd88", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Oas3", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('mu'),1, sep = ""))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Tlr7", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
#VlnPlot(temp3, features = "Marco", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
#VlnPlot(temp3, features = "Cd68", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
#VlnPlot(temp3, features = "Ifi16", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
#VlnPlot(temp3, features = "Csf1r", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b13")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Irf7", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Trim5", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b10")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Sp110", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b6")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Aim2", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

```
```{r}
features <- c("Gzmb", "Prf1", "Bank1", "Casp1", "Il1r2",  "Stat1", "Tnfsf13b", "C1qa", "C1qb", "C3ar1", "Serping1")
Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D0")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "naïve")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 4)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D0")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "Vipex ")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 4)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D3")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D3")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF bad")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 4)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D5")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 4)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D5")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF bad")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 4)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b6")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Casp1", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Bank1", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('nu'),1, sep = ""))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Il1r2", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

temp1 <- PBMC_aggre
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster, start = 1, stop = 1)
Idents(temp1) <- "clus_sym_firstcharacter" 
temp1 <- subset(temp1, idents = "b")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")

temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Bank1", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b2")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Bank1", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

temp1 <- PBMC_aggre
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster, start = 1, stop = 1)
Idents(temp1) <- "clus_sym_firstcharacter" 
temp1 <- subset(temp1, idents = greeks('tau'))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")

temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Stat1", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),7, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Stat1", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
```
Next, Querec et al., 2009.
Start with Il1alpha and CXCL10.
```{r}
features <- c("Il1a", "Cxcl10")
features <- c("Cd14", "Fcgr3")
features <- c("Cd38", "H2-Eb1")
features <- c("Bend4", "Kbtbd7", "Tnfrsf17", "Tpd52", "Nap1l2", "Pfkfb3")
features <- c("Ddx58", "Eif2ak2", "Ifih1", "Jun", "Lamp3", "Siglec1")
features <- c("Rgs1", "Cd69", "Aldh3b1", "Ackr3", "Asgr2", "Slc2a6", "Mef2a", "Ctbp1", "Itgal", "Eif2ak4")

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D0")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "Vipex ")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 5)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D3")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 3)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D5")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 3)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D7")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 3)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('mu'),1, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
#temp2 <- subset(temp2, subset = time != "D5"); 
#temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Cd14", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Fcgr3", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('n'),1, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
#temp2 <- subset(temp2, subset = time != "D5"); 
#temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Cd14", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Fcgr3", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),2, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Bend4", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),10, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Bend4", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

temp1 <- PBMC_aggre
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster, start = 1, stop = 1)
Idents(temp1) <- "clus_sym_firstcharacter" 
temp1 <- subset(temp1, idents = "b")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")

temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Tpd52", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b6")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Tpd52", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b7")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Tpd52", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b8")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Tpd52", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b9")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Tpd52", pt.size = 0, cols = rep("grey",2)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

temp1 <- PBMC_aggre
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster, start = 1, stop = 1)
Idents(temp1) <- "clus_sym_firstcharacter" 
temp1 <- subset(temp1, idents = "b")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); #temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")

temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Jun", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Cd69", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Itgal", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Eif2ak4", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)

temp1 <- PBMC_aggre
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster, start = 1, stop = 1)
Idents(temp1) <- "clus_sym_firstcharacter" 
temp1 <- subset(temp1, idents = greeks('tau'))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); #temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")

temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
VlnPlot(temp3, features = "Jun", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Rgs1", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Cd69", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),5, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); #temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Ddx58", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),12, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); #temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Itgal", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b5") #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); #temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naïve")
temp3 <- subset(temp3, subset = vax != "YF bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
VlnPlot(temp3, features = "Ctbp1", pt.size = 0, cols = rep("grey",3)) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
```
Generate a combined figure for PBMC.
```{r}
plist <- list()

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),12, sep = ""))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
plist[[1]] <- VlnPlot(temp3, features = "Itgal", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

# Cd69
temp1 <- PBMC_aggre
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster, start = 1, stop = 1)
Idents(temp1) <- "clus_sym_firstcharacter" 
temp1 <- subset(temp1, idents = "b")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")

temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
plist[[2]] <- VlnPlot(temp3, features = "Cd69", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

temp1 <- PBMC_aggre
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster, start = 1, stop = 1)
Idents(temp1) <- "clus_sym_firstcharacter" 
temp1 <- subset(temp1, idents = greeks('tau'))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")

temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
plist[[3]] <- VlnPlot(temp3, features = "Cd69", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),5, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
plist[[4]] <- VlnPlot(temp3, features = "Ddx58", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b8")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
plist[[5]] <- VlnPlot(temp3, features = "Tpd52", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),7, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
plist[[6]] <- VlnPlot(temp3, features = "Stat1", pt.size = 0,cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b6")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
plist[[7]] <- VlnPlot(temp3, features = "Casp1", pt.size = 0,cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('nu'),1, sep = ""))
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
plist[[8]] <- VlnPlot(temp3, features = "Il1r2", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "b6")
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
plist[[9]] <- VlnPlot(temp3, features = "Bank1", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = paste(greeks('tau'),2, sep = "")) #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); temp2 <- subset(temp2, subset = time != "D1")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"
#VlnPlot(temp3, features = "Ifi30", pt.size = 0) + stat_summary(fun.y = median, geom='point', size = 10, colour = "black", shape = 95)
plist[[10]] <- VlnPlot(temp3, features = "Bend4", pt.size = 0, cols = c("#9c9c9c","#143fff")) + stat_compare_means() + NoLegend() + 
  theme(plot.title = element_text(size=0)) +
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

fig1 <- ggarrange(plotlist = plist,ncol=5,nrow=2)
```

Next, Costa Naves et al and Marquadt et al. Both are on NK cells.
```{r}
Idents(PBMC_aggre) <- "cluster" 
temp1 <- subset(PBMC_aggre, idents = "n1") #7, 11, 12
Idents(temp1) <- "time" 
temp2 <- subset(temp1, subset = time != "D30"); temp2 <- subset(temp2, subset = time != "D7")
temp2 <- subset(temp2, subset = time != "D5"); 
#temp2 <- subset(temp2, subset = time != "D3")
temp3 <- subset(temp2, subset = vax != "vipex")
temp3 <- subset(temp3, subset = vax != "naive")
temp3 <- subset(temp3, subset = vax != "bad")
temp3@meta.data$time_vax <- paste(temp3@meta.data$time, temp3@meta.data$vax, sep = "_")

Idents(temp3) <- "time_vax"
DefaultAssay(temp3) <- "RNA"

VlnPlot(temp3, features = "Cd69", pt.size = 0, cols = c("#9c9c9c","#143fff","#143fff")) + stat_compare_means()
VlnPlot(temp3, features = "Fcgr3", pt.size = 0, cols = c("#9c9c9c","#143fff","#143fff")) + stat_compare_means()
```
Next, Hou et al.
This will require the single cell level data (not pseudo-bulked).
Download the data from Zenodo (see the data availability section of the manuscript).
```{r}
#setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_04")
#PBMC_data <- LoadH5Seurat("PBMC_data.h5seurat")
PBMC_data <- NormalizeData(PBMC_data, assay = "RNA")
features <- c("Tnfaip3", "Nfkbia", "Irs2", "Cxcr4", "Bcl3", "Mmp9", "Rel", "Fos", "Hif1a", "Socs3", "Nr4a1", "Ripk2", "Traf6", "Bcl6", "Jak2", "Meis1", "Ccr5", "Pcna", "Uso1", "Tcf4", "Hspa1a", "Nmi", "Ccr1", "Dab2")

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D0")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "Vipex ")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 6)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D1")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 6)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D3")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 6)

Idents(PBMC_data) <- "timepoint" 
temp1 <- subset(PBMC_data, idents = "D5")
Idents(temp1) <- "vax" 
temp1 <- subset(temp1, idents = "YF good")
DefaultAssay(temp1) <- "RNA"
FeaturePlot(temp1, features = features, ncol = 6)

# Dot plot now
features <- c("Tnfaip3", "Nfkbia", "Irs2", "Cxcr4", "Bcl3", "Mmp9", "Rel", "Fos", "Hif1a", "Socs3", "Nr4a1", "Ripk2", "Bcl6", "Ccr5", "Hspa1a", "Nmi", "Ccr1")

temp1 <- PBMC_data
temp1$cluster_symbol1 <- temp1$cluster_symbol
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster_symbol1, start = 1, stop = 1)
Idents(temp1) <- "timepoint" 
temp1 <- subset(temp1, subset = timepoint != "D30"); temp1 <- subset(temp1, subset = timepoint != "D7")
#temp2 <- subset(temp2, subset = time != "D5"); #temp2 <- subset(temp2, subset = time != "D1")
temp1 <- subset(temp1, subset = vax != "vipex")
temp1 <- subset(temp1, subset = vax != "naïve")
temp1 <- subset(temp1, subset = vax != "YF bad")
Idents(temp1) <- "clus_sym_firstcharacter"
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != "i")
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != "e")
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != greeks("phi"))
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != greeks("beta"))

char_sym <- temp1@meta.data$clus_sym_firstcharacter
for (k in 1:length(char_sym)) {
  if (char_sym[k] == "m") {
    char_sym[k] <- "M"
  }
  if (char_sym[k] == "d") {
    char_sym[k] <- "M"
  }
  if (char_sym[k] == greeks("mu")) {
    char_sym[k] <- "M"
  }
  if (char_sym[k] == greeks("nu")) {
    char_sym[k] <- "M"
  }
}

temp1@meta.data$char_sym <- char_sym
temp1@meta.data$char_sym_time <- paste(temp1@meta.data$timepoint, temp1@meta.data$char_sym, sep = "_")

library(RColorBrewer)
DefaultAssay(temp1) <- "RNA"
DotPlot(temp1, features=features, group.by="char_sym_time", cols = "RdBu") 
```
Mantel et al.
```{r}
temp1 <- PBMC_data
temp1@meta.data$clus_sym_firstcharacter <- substr(temp1@meta.data$cluster_symbol1, start = 1, stop = 1)
Idents(temp1) <- "timepoint" 
temp1 <- subset(temp1, subset = timepoint != "D30"); temp1 <- subset(temp1, subset = timepoint != "D7")
#temp2 <- subset(temp2, subset = time != "D5"); #temp2 <- subset(temp2, subset = time != "D1")
temp1 <- subset(temp1, subset = vax != "vipex")
temp1 <- subset(temp1, subset = vax != "naïve")
temp1 <- subset(temp1, subset = vax != "YF bad")
Idents(temp1) <- "clus_sym_firstcharacter"
#temp1 <- subset(temp1, subset = clus_sym_firstcharacter != greeks("tau"))
#temp1 <- subset(temp1, subset = clus_sym_firstcharacter != "b")
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != "i")
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != "m")
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != "n")
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != greeks("phi"))
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != greeks("beta"))
temp1 <- subset(temp1, subset = clus_sym_firstcharacter != greeks("mu"))

temp1@meta.data$char_sym_time <- paste(temp1@meta.data$timepoint, temp1@meta.data$clus_sym_firstcharacter, sep = "_")

features <- c("Ccrl2","Prtn3","Ddx58","Ifi27",
"Ifit2","Epb42","Klf1","Spta1","Tmod1")

library(RColorBrewer)
DefaultAssay(temp1) <- "RNA"
DotPlot(temp1, features=features, group.by="char_sym_time", dot.scale = 15, cols = "RdBu") 
```

```{r}
setwd("C:/Users/budha/Documents/R/YF_complete/YF_report_10")
saveRDS(spleen_aggre, file = "spleen_aggre.rds", compress = "xz")
ndLN1 <- readRDS("C:/Users/budha/Documents/R/YF_complete/YF_report_10/PBMC_aggre.rds")
```


