This markdown performs a crumblr differential abundance analysis of dLN cell-type frequencies.
Each timepoint (D0 through D30) is compared against the pooled vipex internal control, separately
by sex, using dream() mixed models with a MouseID random effect to account for repeated samples
(the Sample column) coming from the same mouse.

Load packages.
```{r}
library(crumblr)
library(variancePartition)
library(tidyverse)
```

load data.
```{r}
dLN_data <- readRDS("./cell_freq/dLN_abundance.rds")
dLN_metadata <- readRDS("./cell_freq/dLN_abundance_metadata.rds")
```

Incorporate the batch metadata.
```{r}
batch <- c()

for (k in 1:dim(dLN_metadata)[1]) {
  tempstring <- strsplit(dLN_metadata$Sample[k], split = "H")
  batch <- c(batch, tempstring[[1]][1])
}

dLN_metadata$Batch <- batch
```

Clean the data and metadata further. remove naive. remove cell types representing less than 0.1%.
```{r}
dLN_metadata$Vax[dLN_metadata$Vax == "Vipex "] <- "Vipex"
dLN_metadata$Vax[dLN_metadata$Vax == "vipex"] <- "Vipex"

# Remove naive
dLN_data <- dLN_data[-which(dLN_metadata$Vax == "naïve"),]
dLN_metadata <- dLN_metadata[-which(dLN_metadata$Vax == "naïve"), ]

# Cluster count matrix: samples x clusters in sample_cluster1, transpose to clusters x samples
counts_mat <- as.matrix(dLN_data)
df_cellCounts <- t(counts_mat)

# Drop clusters below 0.1% of total cells
prop <- rowSums(df_cellCounts) / sum(df_cellCounts) * 100
df_cellCounts <- df_cellCounts[which(prop > 0.1), ]
df_cellCounts <- t(df_cellCounts)
```

Apply the crumblr transformation.
```{r}
cobj <- crumblr(df_cellCounts)
```

Variance partitioning: how much of the variance in dLN cell frequencies is explained by mouse,
timepoint, sex and vaccine-response group.
```{r}
form <- ~ (1 | MouseID) + (1 | Vax) + (1 | Time) + (1 | Sex) + (1 | Batch) 
vp <- fitExtractVarPartModel(cobj, form, dLN_metadata)
plotPercentBars(vp)
```
PCA on the standardised crumblr values.
```{r}
pca <- prcomp(t(standardize(cobj)))
df_pca <- merge(pca$x, dLN_metadata, by = "row.names")

ggplot(df_pca, aes(PC1, PC2, color = Time, shape = Vax)) +
  geom_point(size = 3) +
  theme_classic() +
  theme(aspect.ratio = 1)
```
Hierarchical clustering of samples based on the crumblr-transformed values.
```{r}
heatmap(cobj$E)
```
Differential testing: for each sex and vax fit a dream() mixed model comparing at every time point.
```{r}
dLN_data <- as.data.frame(df_cellCounts)
dLN_celldy_list <- list()
for (s in c("M", "F")) {
  for (t in c("D1", "D3", "D5", "D7", "D30")) {
    for (v in c("YF good", "YF bad")) {
      
      dLN_data_s <- dLN_data[which(dLN_metadata$Sex == s),]
      dLN_metadata_s <- dLN_metadata[which(dLN_metadata$Sex == s), ]
      
      dLN_data_st <- dLN_data_s[which(dLN_metadata_s$Time %in% c("D0", t)),]
      dLN_metadata_st <- dLN_metadata_s[which(dLN_metadata_s$Time %in% c("D0", t)),]
      
      dLN_data_stv <- dLN_data_st[which(dLN_metadata_st$Vax %in% c("Vipex", v)),]
      dLN_metadata_stv <- dLN_metadata_st[which(dLN_metadata_st$Vax %in% c("Vipex", v)),]
      
      dLN_metadata_stv$Vax <- relevel(factor(dLN_metadata_stv$Vax), ref = "Vipex")
  
      cobj_stv <- crumblr(dLN_data_stv)
      fit_stv <- dream(cobj_stv, ~ Vax + (1 | MouseID) + (1 | Batch), dLN_metadata_stv)
      fit_stv <- eBayes(fit_stv)
    
    dLN_celldy_list[[paste(s, t, v, sep = "_")]] <- topTable(fit_stv, coef = paste0("Vax", v), number = Inf)
    }
  }
}

#dLN_celldy_DF <- bind_rows(dLN_celldy_list)
#rownames(dLN_celldy_DF) <- NULL
```
Keep the significant hits, using topTable's own BH-adjusted p-value (adj.P.Val), computed jointly
across all clusters and group-vs-vipex coefficients within each sex's model.
```{r}
dLN_celldy_DF <- dLN_celldy_DF[dLN_celldy_DF$adj.P.Val < 0.05, ]
```
